Cosmic Web

### 2014-01-31 paper/main.tex
new table
new plots in the draft

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. }
\label{table:models}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{align_filament_pos_e1_3S.pdf}
  \includegraphics[width=0.45\textwidth]{align_filament_pos_e3_3S.pdf}\\
  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e1_3S.pdf}
  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e3_3S.pdf}
\end{center}
\caption{Distribution for the alignment.
    \label{fig:alignment}}  
\end{figure*}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:models}}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{lccc}\hline\hline
Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
2$\sigma$ & 0.56 & 0.53 &  0.33\\
3$\sigma$ & 0.51 & 0.51 &  0.46\\
General & 0.54 & 0.52 & 0.40\\\hline
\end{tabular}
\caption{Average values for the cosinus between the three eigenvectors and the vector normal to the orbital plane.
\label{table:mu}}
\end{center}
\end{table}

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
\end{center}
\caption{Overdensity distribution for the pairs in the three samples.
    \label{fig:density}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
\end{center}
\caption{Integrated Fractional Anisotropy distribution for the pairs in the three samples.
    \label{fig:FA}}  
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
\end{center}
\caption{Density and Fractional Anisotropy distribution for the pairs in the general and $3\sigma$ samples.
    \label{fig:FA}}  
\end{figure}
